The use of lithic assemblages for the definition of short-term occupations in hunter-gatherer prehistory

### 2018-04-18 README.Rmd
packrat added

[![Travis-CI Build Status](https://travis-ci.org/jmcascalheira/ShortTermOccupations.svg?branch=master)](https://travis-ci.org/jmcascalheira/ShortTermOccupations)

>>>>

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/jmcascalheira/ShortTermOccupations/commits/master)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.2.4-brightgreen.svg)](https://cran.r-project.org/) 
[![Travis-CI Build Status](https://travis-ci.org/jmcascalheira/ShortTermOccupations.svg?branch=master)](https://travis-ci.org/jmcascalheira/ShortTermOccupations)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)
[![ORCiD](https://img.shields.io/badge/ORCiD-/0000--0003--0321--8892-green.svg)](http://orcid.org/0000-0003-0321-8892)

### 2018-04-18 analysis/paper/paper.Rmd
packrat added

---
title: "The use of lithic assemblages for the definition of short-term occupations in hunter-gatherer prehistory"
author:
  - Nuno Bicho (ICArEHB, University of Algarve)
  - João Cascalheira (ICArEHB, University of Algarve)
date: '`r Sys.Date()`'
output: 
    bookdown::word_document2: #subsistute by pdf_document2 or hmtl_document2 as necessary
      fig_caption: yes
      reference_docx: "../templates/template2.docx" 
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl"
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
---

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  dpi = 900,
  fig.width = 9,
  fig.path = "../figures/"
  )

@@

#Filter variables to show on paper
Dataset2 <- Dataset[c(1,2,12:18)]

#Show Table 2
knitr::kable(Dataset2,
             digits = 2,
             row.names = FALSE,
             caption = "Archaeological data based on variables used in this study"
             )

@@

```{r figure3, fig.cap="Correlation plots between Dimension 1 and 2 (left) and Dimension 3 and 4 (right)"}

>>>>

---
title: "The use of lithic assemblages for the definition of short-term occupations in hunter-gatherer prehistory"
author:
  - Nuno Bicho (ICArEHB, University of Algarve, Faro, Portugal) nbicho@ualg.pt
  - João Cascalheira (ICArEHB, University of Algarve, Faro, Portugal) jmcascalheira@ualg.pt
date: '`r Sys.Date()`'
output: 
    bookdown::word_document2: #subsistute by pdf_document2 or hmtl_document2 as necessary
      fig_caption: yes
      reference_docx: "../templates/template2.docx" 
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl"
abstract: |
  Text of abstract
---

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  dpi = 300,
  fig.width = 9,
  fig.path = "../figures/"
  )

@@

#Filter variables to show on paper
#Dataset2 <- Dataset[c(1,2,12:18)]

#Show Table 2
knitr::kable(Dataset,
             digits = 2,
             row.names = FALSE,
             caption = "Archaeological data based on variables used in this study"
             )

@@

```{r figure3, fig.cap="Correlation plots of variables, between Dimension 1 and 2 (left) and Dimension 3 and 4 (right)"}
